LAGOS lake depth

### 2021-08-04 figures/01_contrasts.Rmd
correct old lagos depth column name

# load LAGOSUS DEPTH
lg_raw <- lagosus_load("depth")$depth$depth
lg <- lg_raw %>%
  mutate(lagos_effort =
    forcats::fct_collapse(lg_raw$lagos_effort,
      bathymetry = "bathymetry",
      other = c("LAGOSNE", "manual", "NLA")))

@@

theme_opts <- theme(axis.title.x = element_blank())
cowplot::plot_grid(
  gg_quantdot(lg, lagos_effort, "lake_maxdepth_m") +
    ylab("Max depth (m) \n") +
    theme_opts +
    theme(axis.text.x = element_blank()),
  gg_quantdot(lg, lagos_effort, "lake_waterarea_ha") +
    scale_y_log10() +
    ylab("Area (ha)") +
    theme_opts +
    theme(axis.text.x = element_blank()),
  gg_quantdot(lg, lagos_effort, "urban_distance") +
    scale_y_log10() +
    ylab("Distance to urban (km)") +
    theme_opts,
  rel_heights = c(0.85, 0.85, 1),  ncol = 1)
```

>>>>

# load LAGOSUS DEPTH
lg_raw <- lagosus_load("depth")$depth$lake_depth
lg <- lg_raw %>%
  mutate(lagos_effort =
    forcats::fct_collapse(lg_raw$lake_depth_effort,
      bathymetry = "bathymetry",
      other = c("LAGOSNE", "LAGOSUS", "NLA")))

@@

theme_opts <- theme(axis.title.x = element_blank())
cowplot::plot_grid(
  gg_quantdot(lg, lake_depth_effort, "lake_maxdepth_m") +
    ylab("Max depth (m) \n") +
    theme_opts +
    theme(axis.text.x = element_blank()),
  gg_quantdot(lg, lake_depth_effort, "lake_waterarea_ha") +
    scale_y_log10() +
    ylab("Area (ha)") +
    theme_opts +
    theme(axis.text.x = element_blank()),
  gg_quantdot(lg, lake_depth_effort, "urban_distance") +
    scale_y_log10() +
    ylab("Distance to urban (km)") +
    theme_opts,
  rel_heights = c(0.85, 0.85, 1),  ncol = 1)
```
